SMASH companion source code repository

### 2018-11-08 analysis/index.Rmd
wflow_publish("index.Rmd")

1. [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)

2. [Comparison of signal denoising methods in Gaussian-distributed data
   sets.](gaussian.mean.est.html)

3. [Application of SMASH to motorcycle acceleration data.](motorcycle.html)

4. [Application of SMASH to ChIP-seq data.](chipseq.html)

>>>>

[**Illustration:** SMASH applied to the "spikes" data set.](spikesdemo.html)

### Comparisons of signal denoising methods in simulated data

1. [Estimating the mean function from Gaussian-distributed
data.](gausshomo.html)

2. Estimating the variance function from Gaussian-distributed data.

3. Poisson-distributed data.

### Illustrative applications

1. [Motorcycle acceleration data.](motorcycle.html)

2. [ChIP-seq data.](chipseq.html)
